A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Thoughts on purpose and conclusion

>>>>

\todo[inline]{Decide on having a 'conclusion' or not. If the section is not
  mandatory and there are no further conclusions than at the end of the
  introduction then I am OK with not having one. However, the paper needs to
  serve a purpose. One is, of course, to be documentation for the annotation.
  Another is to attract people to use this work for their own studies. I would
  even argue that this is the \textit{main} purpose, given that the annotation
  in itself represents to scientific progress. So the paper need to give an
  accurate assessment what this can be used for and what is problematic or
  impossible. ATM this is the only statement in this regard: 'facilitates
  modelling of hemodynamic brain responses correlating with speech-related
  events' and the only indication of purpose is 'additional confound measures'. I
  think this is incongruent with the amount of work and the level of detail of
  this annotation.}
